\begin{thebibliography}{99}
\addcontentsline{toc}{chapter}{Bibliography}

\bibitem{MENTOR} M. Franco, B. Rodrigues, B. Stiller: MENTOR: The Design and Evaluation of a Protection Services Recommender System; 15th International Conference on Network and Service Management (CNSM 2019), Halifax, Canada, October 21-25, pp. 1-7.

\bibitem{GrowthForecast} Gartner: Forecast: Information Security, Worldwide, 2016-2022, 2Q18 Update; August 2018, [On-line] \url{https://www.gartner.com/en/newsroom/press-releases/2018-08-15-gartner-forecasts- worldwide-information-security-spending-to-exceed-124-billion-in-2019}


\bibitem{networkIntents} A. Jacobs, R. Pfitscher, R. Ferreira, L. Granville: Refining network intents for self-driving net- works; SIGCOMM Computer Communication Review, Vol. 48, No. 5, January 2019, pp. 55-63.

\bibitem{growth2} Frost \& Sullivan, Global Cloud Infrastructure as a Service Market Outlook, Forecast to 2023. March 2019; ID: 5761855.

\bibitem{computerScienceStudents}Bureau of Labor Statistics, U.S. Department of Labor, Occupational Outlook Handbook, Software Developers, 
on the Internet at \url{https://www.bls.gov/ooh/computer-and-information-technology/software-developers.html} (visited October 07, 2019).

\bibitem{chatbot_reference}Rahman, Al and Mamun, Abdullah \& Islam, Alma. (2017). Programming challenges of chatbot: Current and future prospective. 75-78. 10.1109/R10-HTC.2017.8288910. 

\bibitem{nlp_reference}E. Cambria and B. White, "Jumping NLP Curves: A Review of Natural Language Processing Research [Review Article]," in IEEE Computational Intelligence Magazine, vol. 9, no. 2, pp. 48-57, May 2014.
doi: 10.1109/MCI.2014.2307227

\bibitem{nlp_deep_google} Andor, D., Alberti, C., Weiss, D., Severyn, A., Presta, A., Ganchev, K., ... \& Collins, M. (2016). Globally normalized transition-based neural networks. arXiv preprint arXiv:1603.06042.

\bibitem{nlu_complete} Braun, D., Hernandez-Mendez, A., Matthes, F., \& Langen, M. (2017, August). Evaluating natural language understanding services for conversational question answering systems. In Proceedings of the 18th Annual SIGdial Meeting on Discourse and Dialogue (pp. 174-185).

\bibitem{chatbot_challenges}Rahman, A. M., Mamun, A. A., \& Islam, A. (2017). Programming challenges of chatbot: Current and future prospective. 2017 IEEE Region 10 Humanitarian Technology Conference (R10-HTC). doi:10.1109/r10-htc.2017.8288910 

\bibitem{recomendationSystem} E. Sula.(2019, August).ProtecDDoS: A Recommender System for Distributed Denial-of-Service Protection Services. 

\bibitem{mannedDB} About Manned.org. (n.d.). Retrieved October 29, 2019, from https://manned.org/info/about.

\bibitem{roff} D. M. Ritchie, The Evolution of the UNIX Time-sharing System (AT\&T Bell Laboratories Technical Journal, Vol. 63, No. 8, October 1984)

\bibitem{amazon_nlu} C. Su, R. Gupta, S. Ananthakrishnan and S. Matsoukas, "A Re-Ranker Scheme For Integrating Large Scale NLU Models," 2018 IEEE Spoken Language Technology Workshop (SLT), Athens, Greece, 2018, pp. 670-676.
doi: 10.1109/SLT.2018.8639519, URL: \url{http://ieeexplore.ieee.org/stamp/stamp.jsp?tp=&arnumber=8639519&isnumber=8639030}

\bibitem{amazon_space}Wu, L., Fisch, A., Chopra, S., Adams, K., Bordes, A., Weston, J.\ 2017.\ StarSpace: Embed All The Things!.\ arXiv e-prints arXiv:1709.03856.

\bibitem{word2vec}Mikolov, T., Chen, K., Corrado, G., Dean, J.\ 2013.\ Efficient Estimation of Word Representations in Vector Space.\ arXiv e-prints arXiv:1301.3781.

\bibitem{NER}Strubell, E., Verga, P., Belanger, D., McCallum, A.\ 2017.\ Fast and Accurate Entity Recognition with Iterated Dilated Convolutions.\ arXiv e-prints arXiv:1702.02098.

\bibitem{domainclassifier}Jozefowicz, R., Vinyals, O., Schuster, M., Shazeer, N., Wu, Y.\ 2016.\ Exploring the Limits of Language Modeling.\ arXiv e-prints arXiv:1602.02410.

\bibitem{formulaDomainClassifier} Kim, Y.-B., Kim, D., Kumar, A., Sarikaya, R.\ 2018.\ Efficient Large-Scale Domain Classification with Personalized Attention.\ arXiv e-prints arXiv:1804.08065.

\bibitem{ddosAttacks} Chen, J., Tang, X., Cheng, J., Wang, F., Xu, R.\ 2019.\ DDoS Attack Detection Method Based on Network Abnormal Behavior in Big Data Environment.\ arXiv e-prints arXiv:1903.11844.

\bibitem{lossFunction} Zhao, H., Gallo, O., Frosio, I., Kautz, J.\ 2015.\ Loss Functions for Neural Networks for Image Processing.\ arXiv e-prints arXiv:1511.08861.

\bibitem{nlpComparisson}DURAN, N., HALL, C., MCCARTHY, P., \& MCNAMARA, D. (2010). The linguistic correlates of conversational deception: Comparing natural language processing technologies. Applied Psycholinguistics, 31(3), 439-462. doi:10.1017/S0142716410000068

\bibitem{spacy} Gardner, M., and 8 colleagues 2018.\ AllenNLP: A Deep Semantic Natural Language Processing Platform.\ arXiv e-prints arXiv:1803.07640.

\bibitem{usageSecurity} Botta, D., Werlinger, R., et all. 2007. Towards understanding IT security professionals and their tools. In Proceedings of the 3rd symposium on Usable privacy and security (SOUPS 07). Association for Computing Machinery, New York, NY, USA, 100-111. DOI:https://doi.org/10.1145/1280680.1280693

\bibitem{NLP_LTSM} Young, T., Hazarika, D., Poria, S., Cambria, E.\ 2017.\ Recent Trends in Deep Learning Based Natural Language Processing.\ arXiv e-prints arXiv:1708.02709.

\bibitem{nosql} Padhy, R. P., Patra, M. R., \& Satapathy, S. C. (2011). RDBMS to NoSQL: reviewing some next-generation non-relational database's. International Journal of Advanced Engineering Science and Technologies, 11(1), 15-30.

\end{thebibliography}

